Clicks and Cliques

### 2018-12-28 papersoul.Rnw
add sampling weights description

Two sources of information are used, data provided by the Knight Foundation and the other from the American Community Survey data from the Census Bureau. This section describes the sources and initial processing of the data, and the main statistical tools used for the analysis.

Data from ACS are comunity variable, computed using sampling weights by Census Bureau. 
When using data from Knight Foundation surveys, the sampling weights need to be taken into
account, if the data comes from only one year then the sampling weight is provided
in the data, when all three year survey data are used, sampling weights are divided by three 
so the total aggregate of each variable still can be consider an estimate of the comunity
total.

@@

Additionally, community level information from the \cite{acs2011} and seven tables of the 2007-2011 American Community Survey 5-Year estimates were obtained to provide a socio-demographic description of each community.

@@

On the other hand, each table from the \cite{acs2011} has a different topic (see Table \ref{des.var}). The information corresponds to community totals for different socio-demographic variables, age group, sex, race, education level, average income, employment, etc. Different proportions, rates or indices were computed from these variables, Table \ref{des.var} presents each table description and which new variables were computed from this information.

@@

tab1 <- cbind(quantile(apply(miss[,orig], 1, mean) ),
            quantile(apply(miss[,reco], 1, mean)),
            quantile(apply(miss[,orig], 2, mean) ),
            quantile(apply(miss[,reco], 2, mean) ) )

@@

>>>>

Two sources of information are used, data provided by the Knight Foundation and the other from the American Community Survey (ACS) data from the Census Bureau. This section describes the sources and initial processing of the data, and the main statistical tools used for the analysis.

@@

@@

Additionally, community level information from the \cite{acs2011} and seven tables of the 2007-2011 ACS 5-Year estimates were obtained to provide a socio-demographic description of each community. Each table from the \cite{acs2011} has a different topic (see Table \ref{des.var}). The information corresponds to community totals for different socio-demographic variables, age group, sex, race, education level, average income, employment, etc. Different proportions, rates or indices were computed from these variables, Table \ref{des.var} presents each table description and which new variables were computed from this information.

@@

# tab1 <- cbind(quantile(apply(miss[,orig], 1, mean) ),
#             quantile(apply(miss[,reco], 1, mean)),
#             quantile(apply(miss[,orig], 2, mean) ),
#             quantile(apply(miss[,reco], 2, mean) ) )

@@

\subsubsection{Sampling weights}
Statistical analysis of data from survey need to make a correct use of sampling weights. Depending of the source of information the type of statistical goal, different sampling weights are used in several statistical methods or summaries.

As mentioned earlier, information from ACS corresponds to tables of comunity totals (e.g. Total of 18 years old women in each community). These variables were already expanded by by Census Bureau, so there is no need to consider sampling weights again. For instance, proportions of age group by gender shown in Figrue \ref{age} are computed directly from ACS data without explicit use of sampling weights.

When using data from Knight Foundation surveys, the sampling weights need to be taken into
account. There are two variables representing sampling weights that should be used depending if data from many communities are used jointly (PROJWT) or computations are done for each community separatedly (WEIGHT) \citep{full2010}. For instance, Figure \ref{pp1} includes data from all communities toghether so PROJWT is used as sampling weight, meanwhile Figure \ref{comu} shows proportions of attachment computed separatedly within each community weighted using WEIGHT variable. Additionally, when all three year survey data are used jointly, sampling weights are divided by three so the total aggregate of each variable still can be consider an estimate of the comunity total.

Finally, sampling weights are not used for cluster analysis nor estimation of random forest models.
